Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-15 paper.tex
rebase

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.}} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.
RRRRRR: the fluting perturbation is observable so we can measure
e.g. wavenumbers but there is no appreciable growth so cannot measure
e.g. growth rate}  
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{$\eta=10^{-4}$}& \multicolumn{2}{c}{$\eta=10^{-3}$} \\
&
Anisotropic &
\rev{Isotropic} &
Anisotropic &
\rev{Isotropic} \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{0.163}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& \rev{23.74}
& \rev{23.52}
& \rev{17.15}
& \rev{17.60}\\
Observed axial wave number $k_{\text{flute}}$
& \rev{$22.93$}
& \rev{$22.30$}
& \rev{$16.05$}
& \rev{$16.05$}\\
Observed axial wave number $k_{\text{kink}}$
& {4.57}
& \rev{4.41}
& {3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& \rev{$1.64 \times 10^{-2}$}
& \rev{1.28}
& \rev{$2.89 \times 10^{-3}$}
& \rev{0.370} \\
\rev{Cumulative Ohmic heat at $t=50$}
& \rev{3.06}
& \rev{2.75} 
& \rev{6.54} 
& \rev{6.27} \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

>>>>

\begin{table*}
  \caption{
%\rev{\sout{Quantitative differences in the observed perturbations between results
%\rev{with} different resistivity values $\eta$. In all measurements the
%anisotropic viscosity model is used except for $k_\text{kink}$ where the
%isotropic viscosity model us used. Measurements times are listed in the main
%text.}}
Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.}  
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{$\eta=10^{-4}$}& \multicolumn{2}{c}{$\eta=10^{-3}$} \\
&
Anisotropic &
\rev{Isotropic} &
Anisotropic &
\rev{Isotropic} \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{0.163}\\
\midrule
\rev{Predicted axial wave number $k_{\text{flute}}$}
& \rev{23.74}
& \rev{23.52}
& \rev{17.15}
& \rev{17.60}\\
Observed axial wave number $k_{\text{flute}}$
& \rev{$22.93$}
& \rev{$22.30$}
& \rev{$16.05$}
& \rev{$16.05$}\\
Observed axial wave number $k_{\text{kink}}$
& {4.57}
& \rev{4.41}
& {3.44}
& \rev{3.49}\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& \rev{$1.64 \times 10^{-2}$}
& \rev{1.28}
& \rev{$2.89 \times 10^{-3}$}
& \rev{0.370} \\
\rev{Cumulative Ohmic heat at $t=50$}
& \rev{3.06}
& \rev{2.75} 
& \rev{6.54} 
& \rev{6.27} \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}
